Supplimentary Analysis

### 2021-11-13 Supplymentary.Rmd
* Longtables are visible

---
title: "Supplimentary Analysis"
output: pdf_document
---

```{r options, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600)
set.seed(123)
par(family = "Helvetica")
```

@@

```{r MinResTab}
papaja::apa_table(minresTab, align = "c", caption = "Factor loadings and communality of the retained items(Minmum Residual)", note = "Only loading higher than .30 is reported", font_size = "small")

@@

```{r sixFacTab}
papaja::apa_table(sixFac, align = "c", caption = "Factor loadings and communality of the retained items(six factor)", note = "Only loading higher than .30 is reported", font_size = "small")
```

@@

```{r tabDesAppB, results='asis'}
apa_table(Des.combined, caption = "Descriptive Statistics for Unmerged response options", align = "c", note = "*p<.001", placement = "h")
```

@@

```{r figCorAppB, fig.align='center', fig.cap="Correlation plot of the items",  out.width="100%"}

@@

```{r facIdFigAppB, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot', warning=FALSE}
cowplot::plot_grid(parallel, scree.plot, labels = "AUTO",ncol=1, label_size = 8,align = "v")

@@

apa_table(efa.table,align = "c", caption = "Factor loadings and communality of the retained items [Unmerged Responses]", note = "Only loading higher than .30 is reported", font_size = "small", longtable =T)
```

@@

```{r EFAResidualsAppB,  fig.align='center', fig.cap=' Histogram of residulas:  five-factor solution', warning=FALSE,  results='asis'}
hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))
abline(h =35, lwd = 2, lty = 2)
abline(v =.05,lwd = 2, lty = 2)

>>>>

---
title             : "Supplementary"
shorttitle        : "SA"

author: 
  - name          : "Mushfiqul Anwar Siraji"
    affiliation   : "1, *"
    email         : "mushfiqul.anwarsiraji@monash.edu"
    role:         
      - Formal Analysis
      - Visualization
      - Writing – original draft
      - Writing – review & editing;

  - name          : "Rafael Robert Lazar"
    affiliation   : "2, 3, *"
    role:
      - Data curation
      - Investigation
      - Project administration
      - Visualization
      - Writing – original draft
      - Writing – review & editing;

  - name          : "Juliëtte	van Duijnhoven"
    affiliation   : "4"
    email         : "j.v.duijnhoven1@tue.nl"
    role:         
      - Conceptualization
      - Methodology
      - Investigation
      - Writing – review & editing

  - name          : "Luc Schlangen"
    affiliation   : "5"
    email         : "l.j.m.schlangen@tue.nl"
    role:         
      - Conceptualization
      - Methodology
      - Investigation
      - Writing – review & editing

  - name          : "Shamsul Haque"
    affiliation   : "1"
    email         : "shamsul@monash.edu"
    role:         
      - Conceptualization
      - Supervision
      - Writing – review & editing

  - name          : "Vineetha Kalavally"
    affiliation   : "6"
    email         : "vineetha@monash.edu"
    role:         
      - Supervision
      - Writing – review & editing

  - name          : "Céline Vetter"
    affiliation   : "7, 8"
    email         : "celine.vetter@colorado.edu"
    role:         
      - Conceptualization
      - Writing – review & editing

  - name          : "Gena Glickman"
    affiliation   : "9"
    email         : "gena.glickman@usuhs.edu"
    role:         
      - Conceptualization
      - Methodology
      - Writing – review & editing

  - name          : "Karin Smolders"
    affiliation   : "10"
    email         : "k.c.h.j.smolders@tue.nl"
    role:         
      - Conceptualization
      - Methodology
      - Writing – review & editing

  - name          : "Manuel Spitschan"
    corresponding : yes
    affiliation   : "11, 2, 3"
    email         : "manuel.spitschan@psy.ox.ac.uk"
    role:         
      - Conceptualization
      - Data curation
      - Investigation
      - Project administration
      - Visualization
      - Methodology
      - Writing – original draft
      - Writing – review & editing

affiliation:
  - id            : "1"
    institution   : "Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
  - id            : "2"
    institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"
  - id            : "3"
    institution   : "University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland"
  - id            : "4"
    institution   : "Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands"
  - id            : "5"
    institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Intelligent Lighting Institute, Eindhoven, Netherlands"
  - id            : "6"
    institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Malaysia, Selangor, Malaysia"
  - id            : "7"
    institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"
  - id            : "8"
    institution   : "Ximes GmbH, Frankfurt, Germany"
  - id            : "9"
    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
  - id            : "10"
    institution   : "Eindhoven University of Technology, Human-Technology Interaction Group, Eindhoven, Netherlands"
  - id            : "11"
    institution   : "University of Oxford, Department of Experimental Psychology, Oxford, UK"
  - id            : "*"
    institution   : "Joint first author"

bibliography      : ["references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    latex_engine: xelatex
    includes:
      in_header: header.tex

mainfont: Arial
---

```{r options, warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600)
set.seed(123)
par(family = "Arial")
```

@@

```{r MinResTab}
papaja::apa_table(minresTab,  caption = "Factor loadings and communality of the retained items(Minmum Residual)", note = "Only loading higher than .30 is reported", longtable=T)

@@

```{r sixFacTab, results='asis'}
papaja::apa_table(sixFac,  caption = "Factor loadings and communality of the retained items(six factor)", note = "Only loading higher than .30 is reported",longtable =T)
```

@@

```{r tabDesAppB, results='asis'}
apa_table(Des.combined, caption = "Descriptive Statistics for Unmerged response options",  note = "*p<.001", longtable =T)
```

@@

```{r figCorAppB,  fig.cap="Correlation plot of the items",  out.width="100%"}

@@

```{r facIdFigAppB,  fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot', warning=FALSE}
cowplot::plot_grid(parallel, scree.plot, labels = "AUTO",ncol=1, label_size = 8,align = "v")

@@

apa_table(efa.table, caption = "Factor loadings and communality of the retained items [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T)
```

@@

```{r EFAResidualsAppB,   fig.cap=' Histogram of residulas:  five-factor solution', warning=FALSE,  results='asis'}
hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))
abline(h =35, lwd = 2, lty = 2)
abline(v =.05,lwd = 2, lty = 2)
